|

### 2022-12-02 ms/ms.Rmd

When compared with other large finished bifaces in the region, the distinctive parallel oblique flake scar patterns on both faces of the elliptical bifaces for all, or virtually all, of their length is unique (Figure \ref{fig:illustration}). The absence of identified preforms for this artifact type makes technological and/or attribute-based discriminations related to manufacture a challenge; however, one potential preform was recovered from mortuary contexts at Belcher Mound (Figure \ref{fig:illustration}c). The projection of ritual and/or symbolic interpretation/s that articulate with this flake scar pattern is not possible at this time. Parallel oblique flake scar patterns are known to be characteristic of Guerrero arrow points found at missions in Texas \citep{RN9610}, several dart point types of the late Paleoindian period \citep{RN8584,RN7935,RN11182, RN9843,RN8143,RN10117,RN11181}, and this distinctive flaking pattern has also been inferred from ceramic motifs in Peru \citep{RN7938}.

Parallel oblique flake scar patterns are not characteristic of any of the larger bifaces and bifacial knives in the American Southeast; thus, technological, cultural, or symbolic relationships between the elliptical bifaces and Guerrero arrow points or Angostura dart points are not suggested here. The technological choice to use parallel oblique flaking in finishing these elliptical bifaces most likely represents, at minimum, a stylistic choice by knappers limited to this specific implement; although, that may have been a functionally-relevant choice given their shape and size. In some respects, the decision to employ parallel oblique flaking is as distinctive as the presence---although not diagnostic \citep{RN6170}---of the flat and expanding flake scar pattern observed on Gahagan and Copena bifaces.

>>>>

When compared with other large finished bifaces in the region, the distinctive parallel oblique flake scar patterns on both faces of the elliptical bifaces for all, or virtually all, of their length is unique (Figure \ref{fig:illustration}). The absence of identified preforms for this artifact type makes technological and/or attribute-based discriminations related to manufacture a challenge; however, one potential preform was recovered from mortuary contexts at Belcher Mound (Figure \ref{fig:illustration}c). The projection of ritual and/or symbolic interpretation/s that articulate with this flake scar pattern is not possible at this time. Parallel oblique flake scar patterns are known to be characteristic of several dart point types of the late Paleoindian period \citep{RN8584,RN7935,RN11182, RN9843,RN8143,RN10117,RN11181}, and has even been inferred from ceramic motifs in Peru \citep{RN7938}.

Parallel oblique flake scar patterns are not characteristic of larger bifaces and bifacial knives in the American Southeast; thus, technological, cultural, or symbolic relationships between the elliptical bifaces and Angostura/Paleoindian dart points are not suggested here. The technological choice to use parallel oblique flaking in finishing the elliptical bifaces most likely represents, at minimum, a stylistic choice by knappers limited to this specific implement; although, that may have been a functionally-relevant choice given their shape and size. In some respects, the decision to employ parallel oblique flaking is as distinctive as the presence---although not diagnostic \citep{RN6170}---of the flat and expanding flake scar pattern observed on Gahagan and Copena bifaces.
